Are parental care induced gene expression patterns affect more by internal cues or external stimuli?

### 2019-09-06 docs/manipulation_manuscript.Rmd
more abstract

---
title: Are parental care induced gene expression patterns affect more by internal cues or external stimuli?
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

## Elucidate cause of transcription & protein changes during parental care transitions

@@

### Give birds eggs

@@

### Prolong incubation

@@

### Extend time of hatching

@@

### Remove eggs or chicks

@@

@@

### Reduce time to hatching

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

>>>>

---
title: Are parental care induced gene expression patterns affect more by internal cues or external stimuli?
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  Are parental care induced gene expression patterns affect more by internal cues or external stimuli? We test two alternative hypothesis: internal clock cues versus external offspring stimuli by manipulating the timing of normal transitions during parental care. When we removed offpsring, we find the most pronounces chagnes in gene expression later during incubation or right after hatch, compared to early removeal of eggs. Given the similarity in gene expression the days immediately preceeding and immedately following hatch, we do not have the power to say weether gene expression patters are more like hatch or incuabtion when dummmy egg are used to extend incubation. This matters because...
author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

@@

@@

@@

@@

@@

# Results

@@

### 2019-09-06 docs/manipulation_manuscript.tex
more abstract

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Are parental care induced gene expression patterns affect more by
internal cues or external stimuli?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

@@

\hypertarget{elucidate-cause-of-transcription-protein-changes-during-parental-care-transitions}{%
\subsection{Elucidate cause of transcription \& protein changes during
parental care
transitions}\label{elucidate-cause-of-transcription-protein-changes-during-parental-care-transitions}}

@@

\hypertarget{give-birds-eggs}{%
\subsubsection{Give birds eggs}\label{give-birds-eggs}}

@@

\hypertarget{prolong-incubation}{%
\subsubsection{Prolong incubation}\label{prolong-incubation}}

@@

\hypertarget{extend-time-of-hatching}{%
\subsubsection{Extend time of hatching}\label{extend-time-of-hatching}}

@@

\hypertarget{remove-eggs-or-chicks}{%
\subsubsection{Remove eggs or chicks}\label{remove-eggs-or-chicks}}

@@

@@

\hypertarget{reduce-time-to-hatching}{%
\subsubsection{Reduce time to hatching}\label{reduce-time-to-hatching}}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Are parental care induced gene expression patterns affect more by
internal cues or external stimuli?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
The one question saught. Here we do. What we found. How it matters.

@@

@@

@@

@@

@@

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@
